---
title: "Time Series Recreation"
output: word_document
---

Read data from "A Little Book of R for Time Series" example.

```{r}
kings <- scan("http://robjhyndman.com/tsdldata/misc/kings.dat",skip=3)
```

Turn the df into a ts object.

```{r}
kingsts <- ts(kings)
```

Plot the data to get an idea of the structure.

```{r}
plot.ts(kingsts)
```

Import the TTR library and smooth out the data using a moving average since the data appears to be non-seasonal.

```{r}
library("TTR")
kingstsSMA3 <- SMA(kingsts,n=3)
plot.ts(kingstsSMA3)
```

Change the order to a higher order to smooth out the random fluctuations further.

```{r}
library("TTR")
kingstsSMA8 <- SMA(kingsts,n=8)
plot.ts(kingstsSMA8)
```

Change methods and use differencing.

```{r}
kingstsDiff1 <- diff(kingsts, differences = 1)
plot.ts(kingstsDiff1)
```

This now shows us that the data is stationary and an ARIMA model can be applied.

```{r}
acf(kingstsDiff1, lag.max = 20)
acf(kingstsDiff1, lag.max = 20, plot = FALSE)
pacf(kingstsDiff1, lag.max = 20)
pacf(kingstsDiff1, lag.max = 20, plot = FALSE)
```

Here we can see that we shoud use a Q of 1 or a P of 3. The principle of parsimony led the author's to choose the ARMA(0,1) model. Including the single differencing we come out to ARIMA(0,1,1).

```{r}
kingsArima011 <- arima(kingsts, order = c(0,1,1))
kingsArima011
```

Import the "forecast" package and forecast then plot the ARIMA model's predictions.

```{r}
library("forecast")
kingstsForecast <- forecast(kingsArima011, h=5)
kingstsForecast
autoplot(kingstsForecast)
```

The authors also plot the variance and residuals to determine if the errors or normally distributed with a mean of zero and constant variance. I am unable to run the plotForecastErrors function and cannot find documentation for it in the forecast package.

```{r}
plot.ts(kingstsForecast$residuals)
#plotForecastErrors(kingstsForecast$residuals)
```

